Discrete Quantum Theories and Computing

### 2019-02-02 dissertation.tex
dissertation.lyx "Chapter 5 Toward a Quantum Measurement Theory with Error: Quantum Interval-Valued Probability" Reviewed...

\begin{proof}Consider expressing the observable~$\mathbf{O}$ in
the spectral decomposition specialized to compute the expectation
value relative to a QIVPM, $\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}$,
where $\lambda_{N^{-}}^{-}<\cdots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\cdots<\lambda_{N^{+}}^{+}$
and each $P_{i}^{s}$ is the projector onto the eigenspace of distinct
eigenvalue~$\lambda_{i}^{s}$. Since $\mathbf{O}$ can be diagonalized
by an orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$,
each $P_{i}^{s}$ can be expressed as the sum of some projectors formed
by the elements in $\Omega$, i.e., there is a subset $E_{i}^{s}\subseteq\Omega$
such that $P_{i}^{s}=\sum_{\ket{j}\in E_{i}^{s}}\proj{j}=\varphi\left(E_{i}^{s}\right)$.
To compute the expectation values, we want to not only map $E_{i}^{s}$
to $P_{i}^{s}$ but also map the other ingredients of the expectation
values, including the accumulative sets or projectors, their measures,
and their differences:
\begin{subequations}
\begin{eqnarray}
 &  & P_{i\uparrow}^{s}=\sum_{j\ge i}P_{j}^{s}=\sum_{j\ge i}\sum_{\ket{k}\in E_{j}^{s}}\proj{k}=\sum_{\ket{k}\in\bigcup_{j\ge i}E_{j}^{s}}\proj{k}=\varphi\left(\bigcup_{j\ge i}E_{j}^{s}\right)=\varphi\left(E_{i\uparrow}^{s}\right)\,,\nonumber \\
 &  & \mu^{t}\left(P_{i\uparrow}^{s}\right)=\mu^{t}\left(\varphi\left(E_{i\uparrow}^{s}\right)\right)=\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)\,,\label{eq:pullback-real-measures}\\
 &  & \begin{aligned}\Delta\mu^{t}\left(P_{i\uparrow}^{s}\right) & =\mu^{t}\left(P_{i\uparrow}^{s}\right)-\mu^{t}\left(P_{\left(i+1\right)\uparrow}^{s}\right)=\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)-\left(\varphi^{*}\mu^{t}\right)\left(E_{\left(i+1\right)\uparrow}^{s}\right)\\
 & =\Delta\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)\,,
\end{aligned}
\label{eq:pullback-differences}
\end{eqnarray}
\end{subequations}
where $t\in\left\{ \symrmL,\symrmR\right\} $ and $\left[\mul\left(P\right),\mur\left(P\right)\right]=\bar{\mu}\left(P\right)$
as in Defs.~\ref{def:Choquet} and~\ref{def:expectation-values-QIVPM}.
Notice that Eq.~(\ref{eq:pullback-real-measures}) and~(\ref{eq:pullback-differences})
were simplified to the pullback of $\mul$ and $\mur$ which can be
combined into the pullback of $\bar{\mu}$ as follows: 
\begin{equation}
\begin{aligned}\left[\left(\varphi^{*}\mul\right)\left(E\right),\left(\varphi^{*}\mur\right)\left(E\right)\right] & =\left[\mul\left(\varphi\left(E\right)\right),\mur\left(\varphi\left(E\right)\right)\right]=\bar{\mu}\left(\varphi\left(E\right)\right)\\
 & =\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\left[\left(\varphi^{*}\bar{\mu}\right)^{\symrmL}\left(E\right),\left(\varphi^{*}\bar{\mu}\right)^{\symrmR}\left(E\right)\right]
\end{aligned}
\label{eq:pullback-interval-measures}
\end{equation}
for all $E\subseteq\Omega$.

@@

Since Def.~\ref{def:expectation-values-QIVPM} is an extension of
both quantum real expectation value and classical interval expectation
value, not only the property of quantum real expectation value could
be extended to the previous lemma, but the properties of classical
interval expectation value, like Eq.~(\ref{eq:classical-real-interval-Choquet})
and Thm.~\ref{thm:Rosenmuller}, could be extended to quantum interval
expectation value as well. In particular, Eq.~(\ref{eq:classical-real-interval-Choquet})
can be extended to the following lemma.

@@

We then want to show the expectation value relative to a QIVPM generalizes
the one relative to a classical IVPM by proving a quantum version
of Thm.~\ref{thm:Rosenmuller}. However, since Lemma~\ref{lemma:density-matrix-pullback}
hasn't established enough correspondence between classical and quantum
cores, this theorem is weaker than its classical counterpart.

@@

\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\bar{\mu}\right)=\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\,,
\end{equation}
where $\varphi\colon2^{\Omega}\rightarrow\events$ is defined by Eq.~(\ref{eq:pullback-function}).
Hence, to prove Eq.~(\ref{eq:quantum-interval-expectation-core}),
it is sufficient to prove
\begin{equation}
\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\subseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core-1}
\end{equation}
Since $\events_{\Omega}$ contains all projectors $P_{i}^{s}$ no
matter how $\Omega$ is picked, $\events_{\Omega}$ is one of the
possible choices of $\eventsC$. Thus, if Eq.~(\ref{eq:quantum-interval-expectation-core-1})
is true, and we can also prove
\begin{equation}
\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\supseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,,\label{eq:quantum-interval-expectation-core-supseteq}
\end{equation}
we then have Eq.~(\ref{eq:quantum-interval-expectation-core-equal}).

@@

Now let us consider relaxing $\mathscr{I}$ to a countable set of
finite-width intervals. As the intervals in the image of a QIVPM become
less and less sharp, we expect more and more states to be consistent
with it. In the limit of minimal sharpness, all states~$\rho$ are
consistent with the QIVPM 
\begin{equation}
\bar{\mu}\left(P\right)=\begin{cases}
\imposs & \textrm{ if }P=\mathbb{0}\,;\\
\necess & \textrm{ if }P=\mathbb{1}\,;\\
\unknown=\left[0,1\right] & \textrm{ otherwise}
\end{cases}
\end{equation}
mapping nearly all projections to the \emph{unknown} interval~\unknown.
There is however a subtlety: as shown in the theorem below, it is
possible for an arbitrary assignment of intervals to projectors to
be globally inconsistent.

% \noindent For general QIVPMs mapping to imprecise intervals, we also
% want to seek a simple rule to construct them, and to understand which
% states are consistent with them. However, if measurement intervals are
% too imprecise, the state consistent with the results of measurements
% on some projectors might contradict the state induced by some other
% projectors. Indeed we can formally prove that, in general, there may
% be \emph{no} state consistent with some arbitrary QIVPM.

Like how we proved Thm.~\ref{cor:Kochen-Specker-IVPM}, we need other
two lemmas to simplify the proof of the convexity condition.

@@

\begin{proof}The most important part of the proof is to verify the
convexity condition for $\bar{\mu}$. Given a pair of commuting projectors
$P_{0}$ and $P_{1}$ on a three-dimensional Hilbert space, they can
be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider the function $\varphi\colon2^{\Omega}\rightarrow\events$
defined in Eq.~(\ref{eq:pullback-function}), there are two set of
basis vectors $E_{0}$ and $E_{1}\subseteq\Omega$, such that $\varphi\left(E_{0}\right)=P_{0}$
and $\varphi\left(E_{1}\right)=P_{1}$. Since $E_{0}$ and $E_{1}$
are both subsets of a three-element set, their relation has only three
possibilities. The first possibility is that one of them is a subset
of the other one, $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$.
The second possibility is that they are disjoint, $E_{0}\cap E_{1}=\emptyset$.
If neither of the previous possibilities is true, i.e., they have
some intersections, but not a subset relation, then $E_{0}\cap E_{1}$,
$E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$ are all non-empties.
Together with the fact that $\Omega$ has only three elements, they
are all singleton sets.
\begin{itemize}
\item When one of them is a subset of the other one, say $E_{0}\subseteq E_{1}$,
we have $P_{0}P_{1}=\varphi\left(E_{0}\cap E_{1}\right)=P_{0}$ and
$P_{0}+P_{1}-P_{0}P_{1}=P_{1}$. Thus,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(P_{1}\right)+\bar{\mu}\left(P_{0}\right)\,.
\end{equation}
\item When $E_{0}\cap E_{1}=\emptyset$, we have $P_{0}P_{1}=\varphi\left(E_{0}\cap E_{1}\right)=\mathbb{0}$
and 
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion-3}
\end{equation}
by Eq.~(\ref{amr-1}).
\item When $E_{0}\cap E_{1}$, $E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$
are all singleton sets, say $E_{0}\backslash E_{1}=\left\{ \ket{0}\right\} $,
$E_{1}\backslash E_{0}=\left\{ \ket{1}\right\} $, and $E_{0}\cap E_{1}=\left\{ \ket{2}\right\} $,
proving an equivalent condition for the convexity condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
is easier than proving Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
directly. Since one minus an interval maps this interval to its mirror
image, and reflection preserves the subset relations, the convexity
condition holds if and only if
\begin{equation}
\necess-\bar{\mu}\left(P_{0}P_{1}\right)+\necess-\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)\subseteq\necess-\bar{\mu}\left(P_{0}\right)+\necess-\bar{\mu}\left(P_{1}\right)
\end{equation}
which is equivalent to
\begin{equation}
\bar{\mu}\left(\mathbb{1}-P_{0}P_{1}\right)+\bar{\mu}\left(\mathbb{1}-\left(P_{0}+P_{1}-P_{0}P_{1}\right)\right)\subseteq\bar{\mu}\left(\mathbb{1}-P_{0}\right)+\bar{\mu}\left(\mathbb{1}-P_{1}\right)
\end{equation}
because of Eq.~(\ref{eq:QIVPM-complement}). The last equation holds
because we can apply Eq.~(\ref{amr-1}) on the following chain of
equations:
\begin{equation}
\begin{aligned} & \bar{\mu}\left(\mathbb{1}-P_{0}P_{1}\right)+\bar{\mu}\left(\mathbb{1}-\left(P_{0}+P_{1}-P_{0}P_{1}\right)\right)=\bar{\mu}\left(\proj{0}+\proj{1}\right)+\bar{\mu}\left(\mathbb{0}\right)\\
\subseteq{} & \bar{\mu}\left(\proj{0}\right)+\bar{\mu}\left(\proj{1}\right)=\bar{\mu}\left(\mathbb{1}-P_{0}\right)+\bar{\mu}\left(\mathbb{1}-P_{1}\right)\,.
\end{aligned}
\end{equation}
\end{itemize}
Since the convexity condition holds for all three possibilities, $\bar{\mu}$
is a QIVPM.\end{proof}

@@

After we proved the lemmas, we can state and prove the theorem.

@@

\begin{proof}To prove this theorem, we need to construct a QIVPM
on some Hilbert space and verify that there are no states that are
consistent (see Def.~\ref{def:Consistency}) with it on all possible
events. Assume a Hilbert space of dimension $D=3$ with orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$,
$\ket{\ps'}=\frac{\ket{0}+\ket{2}}{\sqrt{2}}$, and assign 
\begin{equation}
\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
\end{equation}
Consider the map $\bar{\mu}\colon\events\rightarrow\mathscr{I}_{0}$
defined in Table~\ref{tab:non-Born-QIVPM}. We want to prove $\bar{\mu}$
is a QIVPM\@. Since it is easy to verify $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}),
by Lemma~\ref{thm:convex-3-1}, it is sufficient to verify for each
pair of orthogonal states $\ket{\psi'}$ and $\ket{\psi''}$ 
\begin{equation}
\bar{\mu}\left(\proj{\psi'}+\proj{\psi''}\right)\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)\,.\label{amr-2}
\end{equation}
Since $\ket{0}$, $\ket{\ps}$, and $\ket{\ps'}$ are not orthogonal
to each other, at least one of $\bar{\mu}\left(\proj{\psi'}\right)$
and $\bar{\mu}\left(\proj{\psi''}\right)$ is unknown~$\unknown$,
which implies $\unknown\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)$.
Together with the fact that every interval in $\mathscr{I}_{0}$ is
a subset of $\unknown$, Eq.~(\ref{amr-2}) holds, and $\bar{\mu}$
is a QIVPM\@.

@@

\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
a collection of intervals $\mathscr{I}$ including $\imposs$ and
$\necess$, an interval map $\ultramodular\colon\left[0,1\right]\rightarrow\mathscr{I}$
is called ultramodular if: 
\begin{align}
\ultramodular(0)=\imposs\,, &  & \ultramodular(1)=\necess\,, &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,\label{eq:iota-constraints}
\end{align}
and for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have: 
\begin{equation}
\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
\end{equation}
\end{definition}

>>>>

\begin{proof}Consider expressing the observable~$\mathbf{O}$ in
the spectral decomposition specialized to compute the expectation
value relative to a QIVPM, $\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}$,
where $\lambda_{N^{-}}^{-}<\cdots<\lambda_{1}^{-}<0\le\lambda_{1}^{+}<\cdots<\lambda_{N^{+}}^{+}$
and each $P_{i}^{s}$ is the projector onto the eigenspace of distinct
eigenvalue~$\lambda_{i}^{s}$. Since $\mathbf{O}$ can be diagonalized
by an orthonormal basis $\Omega=\{\ket{0},\ket{1},\ldots,\ket{D-1}\}$,
each $P_{i}^{s}$ can be expressed as the sum of some projectors formed
by the elements in $\Omega$, i.e., there is a subset $E_{i}^{s}\subseteq\Omega$
such that $P_{i}^{s}=\sum_{\ket{j}\in E_{i}^{s}}\proj{j}=\varphi\left(E_{i}^{s}\right)$.
To compute the expectation values, we want to not only map $E_{i}^{s}$
to $P_{i}^{s}$ but also map the other ingredients of the expectation
values, including the accumulative sets or projectors, their measures,
and their differences:
\begin{subequations}
\begin{eqnarray}
 &  & P_{i\uparrow}^{s}=\sum_{j\ge i}P_{j}^{s}=\sum_{j\ge i}\sum_{\ket{k}\in E_{j}^{s}}\proj{k}=\sum_{\ket{k}\in\bigcup_{j\ge i}E_{j}^{s}}\proj{k}=\varphi\left(\bigcup_{j\ge i}E_{j}^{s}\right)=\varphi\left(E_{i\uparrow}^{s}\right)\,,\nonumber \\
 &  & \mu^{t}\left(P_{i\uparrow}^{s}\right)=\mu^{t}\left(\varphi\left(E_{i\uparrow}^{s}\right)\right)=\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)\,,\label{eq:pullback-real-measures}\\
 &  & \begin{aligned}\Delta\mu^{t}\left(P_{i\uparrow}^{s}\right) & =\mu^{t}\left(P_{i\uparrow}^{s}\right)-\mu^{t}\left(P_{\left(i+1\right)\uparrow}^{s}\right)=\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)-\left(\varphi^{*}\mu^{t}\right)\left(E_{\left(i+1\right)\uparrow}^{s}\right)\\
 & =\Delta\left(\varphi^{*}\mu^{t}\right)\left(E_{i\uparrow}^{s}\right)\,,
\end{aligned}
\label{eq:pullback-differences}
\end{eqnarray}
\end{subequations}
where $t\in\left\{ \symrmL,\symrmR\right\} $ and $\left[\mul\left(P\right),\mur\left(P\right)\right]=\bar{\mu}\left(P\right)$
as in Defs.~\ref{def:Choquet} and~\ref{def:expectation-values-QIVPM}.
Notice that right-most side of Eq.~(\ref{eq:pullback-real-measures})
and~(\ref{eq:pullback-differences}) are actually the pullback of
$\mul$ and $\mur$ which can be combined into the pullback of $\bar{\mu}$
as follows: 
\begin{equation}
\begin{aligned}\left[\left(\varphi^{*}\mul\right)\left(E\right),\left(\varphi^{*}\mur\right)\left(E\right)\right] & =\left[\mul\left(\varphi\left(E\right)\right),\mur\left(\varphi\left(E\right)\right)\right]=\bar{\mu}\left(\varphi\left(E\right)\right)\\
 & =\left(\varphi^{*}\bar{\mu}\right)\left(E\right)=\left[\left(\varphi^{*}\bar{\mu}\right)^{\symrmL}\left(E\right),\left(\varphi^{*}\bar{\mu}\right)^{\symrmR}\left(E\right)\right]
\end{aligned}
\label{eq:pullback-interval-measures}
\end{equation}
for all $E\subseteq\Omega$.

@@

Since Def.~\ref{def:expectation-values-QIVPM} is an extension of
both quantum real expectation value and classical interval expectation
value, not only the property of quantum real expectation value could
be extended to the previous lemma, but the properties of classical
interval expectation value, like Eq.~(\ref{eq:classical-real-interval-Choquet})
and Thm.~\ref{thm:Rosenmuller}, could be extended to quantum interval
expectation value as well. In particular, Eq.~(\ref{eq:classical-real-interval-Choquet})
can be extended to the following theorem.

@@

Although we can faithfully extend Eq.~(\ref{eq:classical-real-interval-Choquet})
to Thm.~\ref{lemma:expectation-singleton}, this theorem is weaker
than its classical counterpart, Thm.~\ref{thm:Rosenmuller} because
Lemma~\ref{lemma:density-matrix-pullback} hasn't established enough
correspondence between classical and quantum cores.

@@

\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\bar{\mu}\right)=\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\,,
\end{equation}
where $\varphi\colon2^{\Omega}\rightarrow\events$ is defined by Eq.~(\ref{eq:pullback-function}).
Hence, to prove Eq.~(\ref{eq:quantum-interval-expectation-core}),
it is sufficient to prove
\begin{equation}
\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\subseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\eventsC\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core-1}
\end{equation}
Since $\events_{\Omega}$ contains all projectors $P_{i}^{s}$ no
matter how $\Omega$ is picked, $\events_{\Omega}$ is one of the
possible choices of $\eventsC$. Thus, if Eq.~(\ref{eq:quantum-interval-expectation-core-1})
is true, to prove Eq.~(\ref{eq:quantum-interval-expectation-core-equal}),
it is sufficient to verify 
\begin{equation}
\left[\min_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu,\max_{\mu\in\mathrm{core}\left(\varphi^{*}\bar{\mu}\right)}\int\left(\varphi^{*}\mathbf{O}\right)\rmd\mu\right]\supseteq\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}},\max_{\rho\in\coreBorn\left(\bar{\mu},\events_{\Omega}\right)}\expval{\mathbf{O}}_{\muB_{\rho}}\right]\,.\label{eq:quantum-interval-expectation-core-supseteq}
\end{equation}

@@

Now let us consider relaxing $\mathscr{I}$ to a countable set of
finite-width intervals. As the intervals in the image of a QIVPM become
less and less sharp, we expect more and more states to be consistent
with it. In the limit of minimal sharpness, all states~$\rho$ are
consistent with the QIVPM 
\begin{equation}
\bar{\mu}\left(P\right)=\begin{cases}
\imposs & \textrm{ if }P=\mathbb{0}\,;\\
\necess & \textrm{ if }P=\mathbb{1}\,;\\
\unknown=\left[0,1\right] & \textrm{ otherwise}
\end{cases}
\end{equation}
mapping nearly all projections to the \emph{unknown} interval~\unknown.
There is however a subtlety: as we will show in Thm.~\ref{thm:Non-extensible-of-Gleason's}
later, it is possible for an arbitrary assignment of intervals to
projectors to be globally inconsistent, % \noindent For general QIVPMs mapping to imprecise intervals, we also
% want to seek a simple rule to construct them, and to understand which
% states are consistent with them. However, if measurement intervals are
% too imprecise, the state consistent with the results of measurements
% on some projectors might contradict the state induced by some other
% projectors. Indeed we can formally prove that, in general, there may
% be \emph{no} state consistent with some arbitrary QIVPM.
but before proving Thm.~\ref{thm:Non-extensible-of-Gleason's}, we
need other two lemmas to simplify the proof of the convexity condition
again.

@@

\begin{proof}The most important part of the proof is to verify the
convexity condition for $\bar{\mu}$. Given a pair of commuting projectors
$P_{0}$ and $P_{1}$ on a three-dimensional Hilbert space, they can
be diagonalized by a common orthonormal basis $\Omega=\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider the function $\varphi\colon2^{\Omega}\rightarrow\events$
defined in Eq.~(\ref{eq:pullback-function}), there are two set of
basis vectors $E_{0}$ and $E_{1}\subseteq\Omega$, such that $\varphi\left(E_{0}\right)=P_{0}$
and $\varphi\left(E_{1}\right)=P_{1}$. Since $E_{0}$ and $E_{1}$
are both subsets of a three-element set, their relation has only three
possibilities. The first possibility is that one of them is a subset
of the other one, $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$.
The second possibility is that they are disjoint, $E_{0}\cap E_{1}=\emptyset$.
If neither of the previous possibilities is true, i.e., they have
some intersections, but no subset relation, then $E_{0}\cap E_{1}$,
$E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$ are all non-empties.
Together with the fact that $\Omega$ has only three elements, they
are all singleton sets. These three possibilities are going to be
discussed as follow.
\begin{itemize}
\item When one of them is a subset of the other one, say $E_{0}\subseteq E_{1}$,
we have $P_{0}P_{1}=\varphi\left(E_{0}\cap E_{1}\right)=P_{0}$ and
$P_{0}+P_{1}-P_{0}P_{1}=P_{1}$. Thus,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(P_{1}\right)+\bar{\mu}\left(P_{0}\right)\,.
\end{equation}
\item When $E_{0}\cap E_{1}=\emptyset$, we have $P_{0}P_{1}=\varphi\left(E_{0}\cap E_{1}\right)=\mathbb{0}$
and 
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{eq:QuantumInterval-valuedProbability-Inclusion-3}
\end{equation}
by Eq.~(\ref{amr-1}).
\item When $E_{0}\cap E_{1}$, $E_{0}\backslash E_{1}$, and $E_{1}\backslash E_{0}$
are all singleton sets, say $E_{0}\backslash E_{1}=\left\{ \ket{0}\right\} $,
$E_{1}\backslash E_{0}=\left\{ \ket{1}\right\} $, and $E_{0}\cap E_{1}=\left\{ \ket{2}\right\} $,
proving an equivalent condition for the convexity condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
is easier than proving Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
directly. Since one minus an interval maps this interval to its mirror
image, and reflection preserves the subset relations, the convexity
condition holds if and only if
\begin{equation}
\necess-\bar{\mu}\left(P_{0}P_{1}\right)+\necess-\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)\subseteq\necess-\bar{\mu}\left(P_{0}\right)+\necess-\bar{\mu}\left(P_{1}\right)
\end{equation}
which is equivalent to
\begin{equation}
\bar{\mu}\left(\mathbb{1}-P_{0}P_{1}\right)+\bar{\mu}\left(\mathbb{1}-\left(P_{0}+P_{1}-P_{0}P_{1}\right)\right)\subseteq\bar{\mu}\left(\mathbb{1}-P_{0}\right)+\bar{\mu}\left(\mathbb{1}-P_{1}\right)
\end{equation}
because of Eq.~(\ref{eq:QIVPM-complement}). The last equation holds
because we can apply Eq.~(\ref{amr-1}) on the following chain of
equations:
\begin{equation}
\begin{aligned} & \bar{\mu}\left(\mathbb{1}-P_{0}P_{1}\right)+\bar{\mu}\left(\mathbb{1}-\left(P_{0}+P_{1}-P_{0}P_{1}\right)\right)=\bar{\mu}\left(\proj{0}+\proj{1}\right)+\bar{\mu}\left(\mathbb{0}\right)\\
\subseteq{} & \bar{\mu}\left(\proj{0}\right)+\bar{\mu}\left(\proj{1}\right)=\bar{\mu}\left(\mathbb{1}-P_{0}\right)+\bar{\mu}\left(\mathbb{1}-P_{1}\right)\,.
\end{aligned}
\end{equation}
\end{itemize}
Since the convexity condition holds for all three possibilities, $\bar{\mu}$
is a QIVPM.\end{proof}

@@

After we proved the lemmas, we can state and prove the theorem that
some assignment of intervals to projectors can be globally inconsistent..

@@

\begin{proof}To prove this theorem, we need to construct a QIVPM
on some Hilbert space and verify that there are no states that are
consistent (see Def.~\ref{def:Consistency}) with it on all possible
events. Assume a Hilbert space of dimension $D=3$ with orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $, let $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$,
$\ket{\ps'}=\frac{\ket{0}+\ket{2}}{\sqrt{2}}$, and assign 
\begin{equation}
\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
\end{equation}
Consider the map $\bar{\mu}\colon\events\rightarrow\mathscr{I}_{0}$
defined in Table~\ref{tab:non-Born-QIVPM}. We want to prove $\bar{\mu}$
is a QIVPM\@. Since it is easy to verify $\bar{\mu}$ satisfies Eqs.~(\ref{eq:QIVPM-constraints}),
it is sufficient by Lemma~\ref{thm:convex-3-1} to verify 
\begin{equation}
\bar{\mu}\left(\proj{\psi'}+\proj{\psi''}\right)\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)\label{amr-2}
\end{equation}
for each pair of orthogonal states $\ket{\psi'}$ and $\ket{\psi''}$.
Since $\ket{0}$, $\ket{\ps}$, and $\ket{\ps'}$ are not orthogonal
to each other, at least one of $\bar{\mu}\left(\proj{\psi'}\right)$
and $\bar{\mu}\left(\proj{\psi''}\right)$ is unknown~$\unknown$,
which implies $\unknown\subseteq\bar{\mu}\left(\proj{\psi'}\right)+\bar{\mu}\left(\proj{\psi''}\right)$.
Together with the fact that every interval in $\mathscr{I}_{0}$ is
a subset of $\unknown$, Eq.~(\ref{amr-2}) holds, and $\bar{\mu}$
is a QIVPM\@.

@@

\begin{definition}[Ultramodular Functions]\label{def:THOS}Given
a collection of intervals $\mathscr{I}$ including $\imposs$ and
$\necess$, an interval map $\ultramodular\colon\left[0,1\right]\rightarrow\mathscr{I}$
is called ultramodular if
\begin{align}
\ultramodular(0)=\imposs\,, &  & \ultramodular(1)=\necess\,, &  & \ultramodular\left(1-x\right)=\necess-\ultramodular\left(x\right)\,,\label{eq:iota-constraints}
\end{align}
and for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
such that $y=x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have
\begin{equation}
\ultramodular\left(y\right)+\ultramodular\left(x_{2}\right)\subseteq\ultramodular\left(x_{0}+x_{2}\right)+\ultramodular\left(x_{1}+x_{2}\right)\,.\label{eq:iota-Inclusion}
\end{equation}
\end{definition}
